gtsummary

### 2020-12-09 rmarkdown-gtsummary.Rmd
in progress

theme_gtsummary_compact()
```

## Introduction

## Data Summaries

The most common summary needed for research projects are simple summaries of data sets.
To show use of gtsummary functions, we will use a simulated clinical trial data set containing baseline characteristics of 200 patients who received Drug A or Drug B as well as the outcome of tumor response to the treatment.
The data set has label attributes (using the labelled package) for column names.

@@

### `tbl_summary()`

The `tbl_summary()` function can be used to easily create a basic summary statistic table.
This is often the first table of clinical manuscripts and describes characteristics of the cohort under study.
A simple example is shown below with some basic customizations using the function’s main arguments.
Notably, by specifying the “by” argument, you can divide your summary statistic into comparator groups.
In this case, we will split the table by treatment arms.

@@

```{r, echo=FALSE, include = FALSE}
tbl_summary_1 %>% 
  as_gt() %>%
  gtsave(file = "tbl_summary_1.png")
```

\begin{figure}[h!]
  \caption{Simple `tbl\_summary()` example}
  \label{fig:summary_basic}
  \includegraphics[height=5cm]{tbl_summary_1.png}
  \centering
\end{figure}

Figure \ref{fig:summary_basic} is the most bsaic table created with `tbl_summary()`

### `tbl_svysummary()`

### `tbl_cross()`

### `tbl_survfit()`

### Customization

## Model Summaries

### `tbl_regression()`

### `tbl_uvregression()`

## In-line Reporting

## Merging and Stacking

## Themes

## Print Engines

>>>>

theme_gtsummary_compact()
set_gtsummary_theme(list(
  "as_gt-lst:addl_cmds" = list("cols_hide" = rlang::expr(gt::tab_options(table.font.names = "palatino")))
))
```

# Introduction

# Data Summaries

@@

## `tbl_summary()`

@@

```{r, echo=FALSE, include = FALSE}
tbl_summary_1 %>% 
  as_gt() %>%
  gtsave(file = "summary_basic.png")
```

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label`",       "specify the variable labels printed in table",
  "`type`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic`",   "change the summary statistics presented",
  "`digits`",      "number of digits the summary statistics will be rounded to",
  "`missing`",     "whether to display a row with the number of missing observations",
  "`missing_text`","text label for the missing number row",
  "`sort`",        "change the sorting of categorical levels by frequency",
  "`percent`",     "print column, row, or cell percentages"
) %>%
  knitr::kable(caption = "`tbl_summary()` function arguments") 
```

```{r, echo=TRUE}
tbl_summary_2 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt,
              label = age ~ "Patient Age",
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               all_categorical() ~ "{n} / {N} ({p}%)"),
              digits = list(age ~ 2, 
                            all_categorical() ~ c(0, 0, 1)),
              missing = "no")
```

```{r, echo=FALSE, include = FALSE}
tbl_summary_2 %>% 
  as_gt() %>%
  gtsave(file = "summary_plus.png")
```

```{r}
tibble::tribble(
  ~Function,             ~Description,
  "`add_p()`",           "add p-values to the output comparing values across groups",   
  "`add_overall()`",     "add a column with overall summary statistics",   
  "`add_n()`",           "add a column with N (or N missing) for each variable",
  "`add_difference()`",  "add column for difference between two group, confidemce interval, and p-value",
  "`add_stat_label()`",  "add label for the summary statistics shown in each row",   
  "`add_stat()`",        "generic function to add a column with user-defined values",
  "`add_q()`",           "add a column of q values to control for multiple comparisons"   
) %>%
  knitr::kable(caption = "`tbl_summary()` function arguments") 
```

\begin{figure}[h!]
  \caption{Simple `tbl\_summary()` example}
  \label{fig:summary_basic}
  \includegraphics[height=5cm]{summary_basic.png}
  \centering
\end{figure}

## `tbl_svysummary()`

## `tbl_cross()`

## `tbl_survfit()`

## Customization

# Model Summaries

## `tbl_regression()`

## `tbl_uvregression()`

# In-line Reporting

# Merging and Stacking

# Themes

# Print Engines
